The Dark Matter Distribution of the Local Group inferred from Cosmological Simulations: I. The Halo Masses of M31, M33 and the Milky Way

### 2014-12-10 doc/ms1.tex
Placeholder for Marc's likelihood approximation section. Updated author list, it's by no means complete.

\author{Philip J. Marshall\altaffilmark{1}}
\author{Michael T. Busha\altaffilmark{2}} 
\author{Risa H. Wechsler\altaffilmark{3, 4}}
\author{Peter Behroozi\altaffilmark{3}}
\author{XX\altaffilmark{5}}
\author{YY\altaffilmark{6}}
\altaffiltext{1}{Department of Physics, Oxford University, Oxford, OX1 3RH, UK.} 
\altaffiltext{2}{Institute for Theoretical Physics, University of
 Zurich, 8057 Zurich, Switzerland}  
\altaffiltext{3}{Kavli Institute for Particle Astrophysics and Cosmology,
Physics Department, Stanford University, Stanford, CA, 94305, USA
{\tt mbusha@physik.uzh.ch, pjm@slac.stanford.edu, rwechsler@stanford.edu}}
\altaffiltext{4}{Particle and Particle Astrophysics Department, 
SLAC National Accelerator Laboratory, Menlo Park, CA, 94025, USA}
\altaffiltext{5}{XX}
\altaffiltext{6}{YY}

@@

\section{Observational Constraints}
\label{sec:data}

@@

>>>>

\author{Philip J. Marshall\altaffilmark{1}}
\author{Marc Williamson\altaffilmark{1}}
\author{Michael T. Busha\altaffilmark{2}} 
\author{Risa H. Wechsler\altaffilmark{1}}
\author{Peter Behroozi\altaffilmark{3}}
\author{XX\altaffilmark{4}}
\author{YY\altaffilmark{5}}
\altaffiltext{1}{Kavli Institute for Particle Astrophysics and Cosmology, Stanford, CA, 94305, USA
{\tt pjm@slac.stanford.edu, rwechsler@stanford.edu}}
\altaffiltext{2}{???}
\altaffiltext{3}{STScI}
\altaffiltext{4}{YY}

@@

\subsection{Observational Constraints}
\label{sec:data}

@@

\subsection{Approximating the Likelihood}
\label{sec:lhood}

\todo{Marc}{Write this section!}
